---
title: "Comparing to Natasha's PrediXcan Results"
author: "sabrina-mi"
date: "2023-04-04"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---


## BMI without Tail
```{r bmi read results}
bmi_w_tail_assoc = read.table("/Users/sabrinami/Library/CloudStorage/Box-Box/rat-genomic-analysis/PTRS-2023/RatXcan/Results/associations/Br__association_bmi_w_tail.txt", header=TRUE)
hist(bmi_w_tail_assoc$zscore)
```

```{r bmi qq values}
library(tidyverse)
library(qvalue)
qq = qvalue(bmi_w_tail_assoc$pvalue)
bmi_w_tail_assoc$qvalue = qq$qvalues

high_pred_genes = bmi_w_tail_assoc %>% filter(qvalue < 0.05)
```

Read Natasha's result to dataframe
```{r read excel}

library(readxl)
Ac_assoc = read_excel("/Users/sabrinami/Library/CloudStorage/Box-Box/rat-genomic-analysis/PTRS-2023/RatXcan/Results/santhanam-et-al-2022_supplementary-tables-ssr.xlsx", sheet = "ST1 TWAS NAcc", skip=1)

Ac_assoc_bmi_w_tail = Ac_assoc %>% filter(`Metabolic Trait` == "Body Mass Index (BMI) with tail")
```



```{r}
qq_Ac = qvalue(Ac_assoc_bmi_w_tail$`P-value`)
Ac_assoc_bmi_w_tail$qvalue= qq_Ac$qvalues

high_pred_genes_Ac = Ac_assoc_bmi_w_tail %>% filter(qvalue < 0.05)
nrow(high_pred_genes_Ac)
```
651 well-predicted genes

```{r}
Ac_Br_zscores = inner_join(bmi_w_tail_assoc, Ac_assoc_bmi_w_tail, by=c("gene" = "Rat Ensembl ID"))
nrow(Ac_Br_zscores)
Ac_Br_zscores %>% ggplot(aes(zscore, Zscore)) + geom_point() + ggtitle("BMI with Tail PrediXcan z-scores") + xlab("Br") + ylab("Ac") + geom_abline(intercept = 0, slope = 1)
```


## Length with Tail

Br: 5601 genes, Ac: 5388
```{r}
length_w_tail_assoc = read.table("/Users/sabrinami/Library/CloudStorage/Box-Box/rat-genomic-analysis/PTRS-2023/RatXcan/Results/associations/Br__association_length_w_tail_cm.txt", header=TRUE)
hist(length_w_tail_assoc$zscore)
```

```{r}
qq = qvalue(length_w_tail_assoc$pvalue)
length_w_tail_assoc$qvalue = qq$qvalues

high_pred_genes = length_w_tail_assoc %>% filter(qvalue < 0.05)
nrow(high_pred_genes)


Ac_assoc_length_w_tail = Ac_assoc %>% filter(`Metabolic Trait` == "Body length including tail")
```

468 well-predicted genes

```{r}
qq_Ac = qvalue(Ac_assoc_length_w_tail$`P-value`)
Ac_assoc_length_w_tail$qvalue= qq_Ac$qvalues

high_pred_genes_Ac = Ac_assoc_length_w_tail %>% filter(qvalue < 0.05)
nrow(high_pred_genes_Ac)


```
1276 well-predicted genes

```{r}
shared_genes = intersect(high_pred_genes$gene, high_pred_genes_Ac$`Rat Ensembl ID`)
length(shared_genes)
```
91 shared genes with qvalue < 0.05

```{r}
Br_only = setdiff(high_pred_genes$gene, high_pred_genes_Ac$`Rat Ensembl ID`)
length(Br_only)

```
377 genes are high-quality only in Br associations.

```{r}
Ac_only = setdiff(high_pred_genes_Ac$`Rat Ensembl ID`, high_pred_genes$gene)
length(Ac_only)

```
1185 genes are high-quality only in Ac.


```{r compare zscores}
Ac_Br = inner_join(length_w_tail_assoc, Ac_assoc_length_w_tail, by=c("gene" = "Rat Ensembl ID"))
nrow(Ac_Br)
Ac_Br %>% ggplot(aes(zscore, Zscore)) + geom_point() + ggtitle("Length with Tail PrediXcan z-scores") + xlab("Br") + ylab("Ac") + geom_abline(intercept = 0, slope = 1)
```
```{r,eval=FALSE}

Ac_Br %>% ggplot(aes(effect, `Effect Size`)) + geom_point() + ggtitle("Length with Tail PrediXcan Effect Sizes") + xlab("Br") + ylab("Ac") + geom_abline(intercept = 0, slope = 1)
```